Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-20 Markdown Documents/Manuscript.Rmd
new model and plots

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE}
PNames<-rev(unique(dat$ParkName))

@@

mytheme<- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                plot.title = element_text( size=18, color="black",face="bold"),
                axis.title.x = element_text( size=18),
                axis.title.y = element_text( size=18),
                axis.text=(element_text(color="black", size=14)),
                legend.title = element_text(colour="black", size=18),
                legend.text = element_text( size = 14))
```

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=PNames)+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)
```

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
dat%>%filter(UnitCode =="ROMO")%>%
ggplot(.,aes(x=date))+
  geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
  geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
  geom_line(aes(y=RecreationVisits,color="black"),size=1.25)+
  geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
  mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+xlab("Date")+
  scale_color_identity(name = "",
                       breaks = c("black", "#1f78b4"),
                       labels = c("Observed", "Median Estimate"),
                       guide = "legend")+ggtitle("Rocky Mountain National Park")

dat%>%filter(UnitCode == "YOSE")%>%
ggplot(.,aes(x=date))+
  geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
  geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
  geom_line(aes(y=RecreationVisits,color="black"),size=1.25)+
  geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
  mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+xlab("Date")+
  scale_color_identity(name = "",
                       breaks = c("black", "#1f78b4"),
                       labels = c("Observed", "Median Estimate"),
                       guide = "legend")+ggtitle("Yosemite National Park")

dat%>%filter(UnitCode == "ZION")%>%
ggplot(.,aes(x=date))+
  geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
  geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
  geom_line(aes(y=RecreationVisits,color="black"),size=1.25)+
  geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
  mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+xlab("Date")+
  scale_color_identity(name = "",
                       breaks = c("black", "#1f78b4"),
                       labels = c("Observed", "Median Estimate"),
                       guide = "legend")+ggtitle("Zion National Park *not significant")

>>>>

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE}
PNames<-unique(dat$ParkName)

pp<-as.data.frame(posterior_interval(fit))
limits<-row.names(pp[grep("stdsmoke UnitCode",row.names(pp)),])

@@

mytheme<- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                plot.title = element_text( size=18, color="black",face="bold"),
                axis.title.x = element_text( size=18),
                axis.title.y = element_text( size=18),
                axis.text=(element_text(color="black", size=14)),
                legend.title = element_text(colour="black", size=18),
                legend.text = element_text( size = 14))

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=rev(PNames),limits=rev(limits))+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)
```

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "GLAC")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="grey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("black", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Glacier National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())

p2<-dat%>%filter(UnitCode == "GLAC")%>%group_by(Year)%>%
    summarise(meansmoke=mean(Smoke))%>%
    ggplot(.,aes(x=Year,y=meansmoke))+
    geom_segment(aes(xend = Year, yend = 0,color =(meansmoke)),size=1.5) +
    geom_point(aes(color =(meansmoke)),size=5)+
    scale_color_gradient2(low ="#2b83ba" , mid = "#ffffbf", high = "#d7191c",name= "Difference from trend",breaks=c(0.050,-0.035),
                          labels=c("Above","Below")
    ) + 
    #guides(color = FALSE) +
    guides(alpha = FALSE) + 
    theme_classic()+  scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
   scale_y_continuous(name="Smoke (PM 2.5)",expand = c(0, 0), limits = c(0, 1.25e-9))+mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))
```

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "OLYM")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="grey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("black", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Olympic National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())

p2<-dat%>%filter(UnitCode == "OLYM")%>%group_by(Year)%>%
    summarise(meansmoke=mean(Smoke))%>%
    ggplot(.,aes(x=Year,y=meansmoke))+
    geom_segment(aes(xend = Year, yend = 0,color =(meansmoke)),size=1.5) +
    geom_point(aes(color =(meansmoke)),size=5)+
    scale_color_gradient2(low ="#2b83ba" , mid = "#ffffbf", high = "#d7191c",name= "Difference from trend",breaks=c(0.050,-0.035),
                          labels=c("Above","Below")
    ) + 
    #guides(color = FALSE) +
    guides(alpha = FALSE) + 
    theme_classic()+  scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
   scale_y_continuous(name="Smoke (PM 2.5)",expand = c(0, 0), limits = c(0, 1.0e-9))+mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))
```
